### 2017-01-25 conclusion.tex
Revisions made to Conclusion

Plasma irregularities in the \(F\)-region ionosphere have been observed for decades.  However, despite extensive data sets collected over these years, supprisingly little is known about these irregularities, especially at small scales.  This is in part due to the complex and turbulent nature of the ionosphere, particularly in the polar regions, but also due to some of the inherent limitations in traditional observation techniques which can make it very challenging to identify exactly what processes are operational.  In this Chapter, we summarize the results that have previously been discussed in Chapters \ref{sec:paper1}--\ref{sec:paper3}, shown in Figure \ref{fig:conclusion}, and consider what overarching conclusions can be derived from them.  Additionally, Section \ref{sec:futurework} will provide recommendations for future research which will help answer some of the still outstanding questions and further our understanding of small-scale polar \(F\)-region plasma irregularities.

@@

In the polar caps, backscatter is often observed at nighttime even when background plasma density is low and propagation conditions are traditionally thought to be too poor for FAIs to be observed with HF radar.  This implies an additional source of nighttime plasma density that is not easily accounted for by models.  Frequent polar patches that propagate from the dayside to the nightside could be the source of this additional density.  The requirements for confirming this hypotheis will be detailed further in Section \ref{sec:futurework}.

\begin{figure}
  \includegraphics[width=\textwidth]{conclusion.pdf}
  \caption[Irregularity production factors]{Summary of the main conclusions in this thesis as to what factors most effect pasma irregularity production.}
  \label{fig:conclusion}
\end{figure}

Nighttime observations of FAIs is also higher with a positive IMF By component.  This could be due to the control that the By component exerts over ionospheric convection patterns.  In a convectional two-cell convection pattern with predominantly negative IMF Bz, the plasma flows antisunward from dayside to nightside across the terminator.  In this arrangement, the plasma flow, \(\vec{V}_E\), and the density gradient, \(\vec{G}\), are antiparallel, the least favorable orientation for GDI growth.  However, with a significant IMF By component, the orientation of the convection cells rotates such that plasma no longer convects directly antisunward, creating a situation where GDI is more favorable and plasma structures can develop more readily.  Additionally, an IMF By component can contribute to the formation of polar patches by creating convection perturbations that separate high density patches from the daytime reservoir, as described in Section \ref{sec:lit_patches}.  In this way, the IMF By component may be indirectly responsible for the increased observation of backscatter.  If patch occurrence increases, it can contribute to the nighttime background density, as described above, which can improve propagation conditions so that FAIs can be observed by 
HF radars.

@@

The plasma drift and wavevector directions influence the asymmetry that is observed surrounding polar patches.  The direction that the patch is drifting relative to its elongation direction impacts the orientations of \(\vec{G}\) and \(\vec{V}_E\) and controls the GDI growth rate.  This also creates the asymmetry between the different edges of the patch because as the gradient direction changes, the irregularity growth rate changes.  Additionally, linear theory predicts that irregularity growth is anisotropic, so the orientation of the patch relative to the radar can also impact the observed irregularities.  In the \(F\) region, the GDI growth rate is highest for wavevectors perpendicular to the gradient, \(\vec{G}\).  Although plasma waves can occur in all directions, a SuperDARN radar will only observe waves who's wavevectors are parallel to a radar beam.  Because of this, irregularities as well as structure asymmetry are most likely to be maximized if the radar's boresight is parallel to the structure's elongation, Figure \ref{fig:conclusion}.

@@

>>>>

Plasma irregularities in the \(F\)-region ionosphere have been observed for decades.  However, despite extensive data sets collected over these years, surprisingly little is known about these irregularities, especially at small scales.  This is in part due to the complex and turbulent nature of the ionosphere, particularly in the polar regions, but also due to some of the inherent limitations in traditional observation techniques which can make it very challenging to identify exactly what processes are operational.  In this Chapter, we summarize the results that have previously been discussed in Chapters \ref{sec:paper1}--\ref{sec:paper3}, shown in Figure \ref{fig:conclusion}, and consider what overarching conclusions can be derived from them.  Additionally, Section \ref{sec:futurework} will provide recommendations for future research which will help answer some of the still outstanding questions and further our understanding of small-scale polar \(F\)-region plasma irregularities.

@@

Radar backscatter from ionospheric irregularities is most likely to be observed at particular slant ranges in the radar FoV, Figure \ref{fig:conclusion}.  The location of this window of high echo occurrence slant ranges varies diurnally and seasonally, primarily due to changing background plasma density in the ionosphere.  The background density controls how far a radar beam must travel to be perpendicular to the magnetic field through refraction and observe FAIs.  This can create the illusion that small-scale plasma irregularities are more common in certain physical locations while in reality, they may exist over a much wider area but it is easier to observe them in particular locations.

In the polar caps, backscatter is often observed at nighttime even when background plasma density is low and propagation conditions are traditionally thought to be too poor for FAIs to be observed with HF radar.  This implies an additional source of nighttime plasma density that is not easily accounted for by models.  Frequent polar patches that propagate from the dayside to the nightside could be the source of this additional density, Figure \ref{fig:conclusion}.  The requirements for confirming this hypothesis will be detailed further in Section \ref{sec:futurework}.

\begin{figure}
  \includegraphics[width=\textwidth]{conclusion.pdf}
  \caption[Irregularity production factors]{Summary of the main conclusions in this thesis as to what factors most effect small-scale plasma irregularity production.  Polar patches (orange) drift antisunwards across the polar cap following the background plasma convection (red contours).  Nighttime irregularity observation is enhanced with a positive IMF By component.  Production is maximized near the terminator.  Small-scale irregularity production surrounding a large-scale structure is found to exhibit both asymmetry and anisotropy.  Radars are most likely to observe this asymmetry if the patch is elongated along the radar boresight.}
  \label{fig:conclusion}
\end{figure}

Nighttime observations of FAIs is also higher with a positive IMF By component, Figure \ref{fig:conclusion}.  This could be due to the control that the By component exerts over ionospheric convection patterns.  In a convectional two-cell convection pattern with predominantly negative IMF Bz, the plasma flows antisunward from dayside to nightside across the terminator.  In this arrangement, the plasma flow, \(\vec{V}_E\), and the density gradient, \(\vec{G}\), are antiparallel, the least favorable orientation for GDI growth.  However, with a significant IMF By component, the orientation of the convection cells rotates such that plasma no longer convects directly antisunward, creating a situation where GDI is more favorable and plasma structures can develop more readily.  Additionally, an IMF By component can contribute to the formation of polar patches by creating convection perturbations that separate high density patches from the daytime reservoir, as described in Section \ref{sec:lit_patches}.  In this way, the IMF By component may be indirectly responsible for the increased observation of backscatter.  If patch occurrence increases, it can contribute to the nighttime background density, as described above, which can improve propagation conditions so that FAIs can be observed by 
HF radars.

@@

The plasma drift and wavevector directions influence the asymmetry that is observed surrounding polar patches.  The direction that the patch is drifting relative to its elongation direction impacts the orientations of \(\vec{G}\) and \(\vec{V}_E\) and controls the GDI growth rate.  This also creates the asymmetry between the different edges of the patch because as the gradient direction changes, the irregularity growth rate changes.  Additionally, linear theory predicts that irregularity growth is anisotropic, so the orientation of the patch relative to the radar can also impact the observed irregularities because the rate at which irregularities develop changes in different directions.  In the \(F\) region, the GDI growth rate is highest for wavevectors perpendicular to the gradient, \(\vec{G}\).  Although plasma waves can occur in all directions, a SuperDARN radar will only observe waves who's wavevectors are parallel to a radar beam.  Because of this, irregularities as well as structure asymmetry are most likely to be maximized if the radar's boresight is parallel to the structure's elongation, Figure \ref{fig:conclusion}.

@@

The production and characteristics of small-scale plasma irregularities and the factors that control them are complex.  Radar studies must differentiate between production and propagation factors, determining if in fact irregularity production is more favorable or if background conditions just make observations of irregularities more likely.  This thesis helps advance our understanding by identifying a number of situations where small-scale irregularities are observed and establishing plausible reasons why either production is favorable according to plasma theory or radar observation is likely.

### 2017-01-25 introduction.tex
Revisions made to Conclusion

\begin{figure}
	\includegraphics[width=0.5\textwidth]{irregularity.pdf}
	\caption[Plasma irregularities in the polar ionosphere]{Schematic of different scale size plasma density irregularities that occur in the polar cap.  Polar patches, orange, move with the background ionospheric convection, indicated by green contours.  Smaller-scale structures often move develop along the edges of polar patches where strong density gradients exist.  Field-aligned irregularities, FAIs, are density perturbations that form along the magnetic field lines, pink lines.}
	\label{fig:polarirreg}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=0.5\textwidth]{irregularity.pdf}
	\caption[Plasma irregularities in the polar ionosphere]{Plasma density irregularities occur in the polar cap at different scale sizes.  Polar patches, orange, move with the background ionospheric convection, indicated by red contours (a).  Smaller-scale structures often move develop along the edges of polar patches where strong density gradients exist (b).  Intermediate scale irregularities are primarily responsible for disrupting radio signals traveling through the ionosphere (c).  Field-aligned irregularities, FAIs, are density perturbations that form along the magnetic field lines, light blue (d).}
	\label{fig:polarirreg}
\end{figure}
